% Derived from https://www.overleaf.com/project/614e77fa3f38da11edd45b16 Christopher Keyes

\documentclass{Resume}

\usepackage{enumitem}
\usepackage{etaremune}
\usepackage{amsmath}
\usepackage{titlesec}


\begin{document}
\titlespacing*{\section}{0pt}{2.8em}{1em}

\twocolumn[{

\begin{@twocolumnfalse}

\begin{minipage}[t]{0.5\textwidth}
\begin{flushleft}
    % \begin{center} % \name{Hamish Starling}
% \begin{minipage}[t]{0.5\textwidth}
    {\LARGE\textbf{Hamish Starling}}
    hamishstarling@hotmail.co.uk \\
% \end{minipage}
\end{flushleft}    
\end{minipage}
\begin{minipage}[t]{0.5\textwidth}
    \begin{flushright}
            linkedin.com/in/hamish-starling/ \\
            github.com/starswap/            
    \end{flushright}    
\end{minipage}

\vspace{1em}

\end{@twocolumnfalse}}]

% need tof igure out how to not have 20 versions - optional components.
%   Use git branches?
% I'm actually quite impressed with what your interns have produced. It's pretty hard to get a good feel for! 
% For Dynamo DB

% cleint results

% Stuff we could work into the CV
%   Comp Arch Tutorial Winner
%   Duolingo world champion 22 and 1000 day streak
%   Jane street estimathon souii
%   Optiver Ready Trader Go - Got to top 20% / top 200 teams.
%   Korean
%   Website Change Alert
%   Language Proficiency
%   All hackathons; perhaps in a separate seciton:
%       -- Arcadia - BackyardHacks111
%       -- Swapify - HackTheRunway - Best Use of CockroachDB
%       -- Pine Protection - HackThe6ix 2022 - 2nd Place; Best HW Hack/
%       -- GreenShip- ICHack 2022
% edstem prize and top 5 - C project

% For Interviews:
%   See "Softwire Interview 1" Document which also contains extra curriculars notes

% Data Engineering
% Highlight Web Scraping and SQL Experience
%	\section{Academic Interests}
%	Briefly list your primary areas of academic interests here

	\section{Education}
	\textbf{MEng Computing} (Imperial College London) \hfill (2022 - )
 \begin{itemize}
     \item Year 2: \textbf{90.13\%} \textit{Dean's List} \begin{itemize}
         \item Algorithm Design and Analysis \textbf{98.00\%}
         \item Compilers \textbf{98.70\%}
         \item Software Engineering Design \textbf{97.96\%}
         \item French V - Pass with Distinction
     \end{itemize}
     \item Year 1: \textbf{89.01\%} \textit{Dean's List} \begin{itemize}
         \item Computing Practical \textbf{97.23\%}
         \item Korean I - Pass with Distinction
     \end{itemize}
     \item Prizes: \begin{itemize}
         \item Netcraft Second Year Prize (2024)
         \item G-Research Academic Excellence Prize (2024)
         \item Solidatus Excellence in SWE Award (2024)
         \item Netcraft Haskell Prize (2023)
         \item Grocers' Golden Jubilee Scholarship (2022)
     \end{itemize}
 \end{itemize}
		\textbf{A Level} \hfill (2020 - 2022) \\
            % \begin{itemize}
                A*A*A*A*A* in Maths, FM, Physics, CS \& French.
            % \end{itemize}
            
        \section{Experience}
            \textbf{Software Engineer} - Optiver \hfill (Jul - Aug '24)
                \begin{itemize}
                    \item Individually designed and implemented a self-service system for KPI backfilling.
                    \item Monitoring, scheduling triggering and killing UNIX processes across machines via a dashboard UI.
                    % \item Another BP
                \end{itemize}            
            \textbf{Software Developer} - Softwire UK\hfill (Jul - Aug '23)
            \begin{itemize}
                \item React Native / TS app for social impact startup.
                \item I learnt AWS DynamoDB and built the DB schema.
                \item I architected the app's API and integrated with AWS.
                \item Subsequently I continued working on the app to deploy it to production, reaching  $\approx$ 100 families.  

            \end{itemize}

	\section{Statistics \& Machine Learning}
			\textbf{MathWorks Math Modelling (M3) Challenge 2022} 
			\begin{itemize}
                \item Team won Honorable Mention \& Best UK paper in the International Modelling Competition
			    \item My Python code for probability and population \\ simulation modelled remote work trends effectively.
			    \item Presenting our work at Jane Street New York enabled me to develop explanatory and communicative skills.
			\end{itemize}
            \textbf{Online Courses}
                \begin{itemize}
                    \item \textbf{Machine Learning} (Stanford University)
                    \item \textbf{Deep Learning} (Deeplearning.ai)
                \end{itemize}


   			
		% \subsection{Online Courses}
		% 	\begin{itemize}[itemsep=1mm, parsep=0pt]
		% 		\item \textbf{Machine Learning}, Stanford University
		% 		\item \textbf{Deep Learning}, Deeplearning.ai 
		% 		\item \textbf{Fundamentals of Reinforcement Learning} \\ University of Alberta
		% 	\end{itemize}


		\newpage
	\section{Programming}
		Experience: Python, C, C++, Haskell, Java, Kotlin, Scala, HTML/CSS/JS/TS, React (Native), SQL, DynamoDB.
   
		\subsection{Competitive Programming}
			\begin{itemize}
    			    \item \href{https://open.kattis.com/countries/GBR}{Kattis} UK top 10.
    			    \item British Informatics Olympiad 5-time participant.
    			    \item Meta Hacker Cup 2022 \& 2023 global top 1500
                    \item Finalist (57th) in Prologin European competition 2024 
			\end{itemize}
		\subsection{Projects \& Hackathons}
			\begin{itemize}

               \item \textbf{Joint Advanced Student School Cyprus 2024} ``Talking with Smart Cities" - Smart assistant for booking parking spaces in an eGarage, with driverless robots.\\
               \textit{Presented to mock investors from Leptos}
   
            \item \textbf{Lazarus Lightning Detection System} - Microphones and LDRs locate lightning strikes to prevent wildfires.\\ \textit{Imperial Computing 1st Year C Project Top 5}
            
            \item \textbf{``Pine Protection"} - ML \& Hardware solution to defeat Mountain Pine Beetle. (Hack the 6ix 2022)\\ 
            \textit{2nd Place; Best Hardware Hack; Best Use of Protobuf}

            \item \textbf{Machine Learning Python Programming IDE} - RNNs and rule-systems to improve students' Python. \\ \textit{A Level NEA Full Marks project}


            % JASS project
            % Website Change Alert
            % Swapify?

    
				
			\end{itemize}
    
    \section{Cyber Security}
            \textbf{INCS-CoE Country to Country CTF 2023}
            \begin{itemize}
                \item Placed 57th in the world in the qualifiers
                \item Competed at the final at Keio University, Japan
            \end{itemize}
		\textbf{Cyber Discovery Summer School}
				\begin{itemize}
				    \item Top 200 from 30000 students in national programme.
				    \item Attended 3 ``Elite" Summer Camps
				    \item I became a GIAC-Certified Forensic Examiner with \textbf{97\%} in the final exam, and joined the Advisory Board.
				\end{itemize}
            \textbf{UK National Cipher Challenge}
		  \begin{itemize}
                \item 1st= placing (2020), using genetic and hill climbing algorithms, and statistical analysis to crack ciphers.
            \end{itemize}
            
    \section{Skills \& Character}
        \begin{itemize}
            \item \textbf{Dedication \& Tenacity} (M3 and Cipher Challenge) - my approach to failure is to improve and try again.
            \item \textbf{Sharing \& Helping} - ICL "Most Helpful Student" prize; recognised for clear explanations at Softwire. I TA the practical classes at Imperial.
            \item \textbf{Love for Learning} - Particularly MFL
        \end{itemize}
        
%	\footnotetext[0]{Updated \today}
    \pagenumbering{gobble}
\end{document}

