% Derived from https://www.overleaf.com/project/614e77fa3f38da11edd45b16 Christopher Keyes

\documentclass{Resume}

\usepackage{enumitem}
\usepackage{etaremune}
\usepackage{amsmath}



\begin{document}

\twocolumn[

\begin{@twocolumnfalse}

    \begin{center} \name{Hamish Starling} 

    \contact{hamishstarling@hotmail.co.uk}%{}{Github Link}}
    %\contact{(Find out even more on my 
    %\href{https://www.linkedin.com/in/hamish-starling-147859235/
%}{LinkedIn Profile})}%{}{Github Link}}

\end{center}

	\section{Profile}
    An ambitious undergraduate student, with a passion for problem solving, a constant desire to learn, and a curiosity to explore the use of mathematics and computing in industry.
    \\

\end{@twocolumnfalse}
]

% Comp Arch Tutorial Winner
% Duolingo world champion 22
% JAne street estimathon souii

% Add Languages etc - need more info like on LinkedIn (or maybe just link to LinkedIn)
% All hackathons; perhaps in a separate seciton:
% -- Arcadia - BackyardHacks111
% -- Swapify - HackTheRunway - Best Use of CockroachDB
% -- Pine Protection - HackThe6ix 2022 - 2nd Place; Best HW Hack/
% -- GreenShip- ICHack 2022


% Data Engineering
% Highlight Web Scraping and SQL Experience

%	\section{Academic Interests}
%	Briefly list your primary areas of academic interests here

	\section{Education}
		\subsection{Undergraduate - Imperial College London}
		    \-\hspace{2em}\textbf{Computing (AI \& Machine Learning)}
		    \\ \-\hspace{2em}Imperial College London
		    \\ \-\hspace{2em}(2022-2026) \\
		    \\ Worshipful Company of Grocers Golden Jubilee Scholar.\\

		    \textbf{Themes Studied:} Discrete Maths, Databases, Computer Systems, Calculus, Functional Programming, Assembly Programming, Computer Architecture. 


    
		\subsection{Secondary - Watford Boys Grammar School}
		    \subsubsection{A Level (2020-2022)}
		    \textbf{A*A*A*A*A*} in Maths, FM, Physics, CS \& French.
            % \subsubsection{GCSE}		    
            % I achieved ten grade \textbf{9}s and one grade \textbf{8} at GCSE.
%				\begin{itemize}
%					\item GCSE \textbf{Grade 9} in Mathematics, English Lang., French, Spanish, Geography, Biology, Physics, Chemistry, Computer Science, and \textbf{Grade 8} in English Lit.
%					\item AQA Level 2 Certificate in Further Maths, \textbf{Grade 9}
%				\end{itemize}
		\subsection{Cyber Discovery Summer School}
				\begin{itemize}
				    \item Top 200 from 30000 students in national programme.
				    \item I attended three ``Elite" Summer Camps and three CyberFirst courses, gaining Cyber Security knowledge, and winning a CTF with my team.
				    \item I became a GIAC-Certified Forensic Examiner with 97\% in the final exam, and joined the Advisory Board.
				\end{itemize}


	\section{Skills}
			\begin{itemize}
				\item \textbf{Leadership \& Helping Others:} 
				    \begin{itemize}
				        \item President of \textit{Cybersecurity Club} (2019) and \\ \textit{Computing Society} (2021).
				        \item I taught sessions on Wireshark, IoT, Blockchain, REST APIs, Functional Programming and other topics to aspiring young computer scientists.
				    \end{itemize} 
				\item \textbf{Organisation \& Teamwork:} 
				    \begin{itemize}
				        \item Project Manager and Chief Programmer of \\ Go4SET engineering prizewinning team which created an app to offer cheaper alternatives to the weekly shop.
				        \item I organised the team to distribute roles fairly and logically and get the job done, under time and budget constraints.
				    \end{itemize}
				\item \textbf{Dedication \& Tenacity:}
				    \begin{itemize}
				        \item 1st equal placing in University of Southampton's National Cipher Challenge.
				        \item It took 4 years of determined problem solving, often just missing out on the top positions.
				        \item I used genetic and hill climbing algorithms to crack ciphers, persisting in the face of challenge.
				    \end{itemize}
%				\item \textbf{Communication:} 
%				\item problem solvign
			\end{itemize}		

		\newpage
	\section{Techincal Experience}
			Programming and Scripting experience with Python, C++, Haskell, Java, Kotlin, Web and SQL.

		\subsection{Competitive Programming}
%			\begin{itemize}
%				\item UK top 50 on \href{https://open.kattis.com/countries/GBR}{Kattis}
%				\item British Informatics Olympiad Participant last 5 years, top score 59.
%				\item Solved 29 problems on UVa Online Judge and over 80 on Advent of Code.
%			\end{itemize}
			I explore my love for algorithmic problem solving through programming competitions. 
			\begin{itemize}
			    \item I am ranked in the \href{https://open.kattis.com/countries/GBR}{Kattis} UK top 20.
			    \item British Informatics Olympiad 5-time participant.
			    \item Meta Hacker Cup 2022 4th in UK (1028th overall).
%			    \item I placed in Facebook Hacker Cup 2021 top 3000 and Google Code Jam top 3200.
            % UKIEPC 31st place; 6th @ Imperial  : (.

			    
			\end{itemize}
		\subsection{Project Work \& Hackathons}
			\begin{itemize}[itemsep=1mm, parsep=0pt]
				\item \textbf{Alexa School Timetable App} which web scrapes students' timetables from Moodle and provides them over Voice User Interface (VUI).
				\item \textbf{LAMP Recipes Website} for my household, with Optical Character Recognition (OCR) recipe input and saving of recipes via a Chrome Extension.
				\item \textbf{Machine Learning Python Programming IDE} using Recurrent Neural Networks and rule-based systems to improve students' Python programming. % Learnt why decent dev ops tools like docker are worth having - library version control + Releasing my own software and giving it logical version numbers
		%		\item \textbf{AI Chess and Hex games} --- various AI strategies.
				\item \textbf{Clothes Swapping App} for Hack the Runway \\ Hackathon 2022; winner of Best Use of CockroachDB.
				\item \textbf{``Pine Protection"} - ML Model; Hardware Attachment and Web Interface to defeat Mountain Pine Beetle; HT6 2022 2nd Place; Best Hardware Hack \& Best Use of Protobuf.
			\end{itemize}
%			Interested in learning more about one of these projects? You can find them on my \href{https://github.com/starswap}{Github}.

	\section{Statistics \& Machine Learning}
	    Though my main interest is Cyber Security, I've enjoyed exploring Modelling and Machine Learning, through:
			
		\subsection{Online Courses}
			\begin{itemize}[itemsep=1mm, parsep=0pt]
				\item \textbf{Machine Learning}, Stanford University
				\item \textbf{Neural Networks \& Deep Learning}, \\ Deeplearning.ai 
				% \item \textbf{Fundamentals of Reinforcement Learning}, \\ University of Alberta (Part way through)
			\end{itemize}

		\subsection{International Modelling Competition}
			\textbf{MathWorks Math Modelling Challenge 2022} 
			\begin{itemize}
			    \item Honorable Mention \& Best UK paper.
			    \item My Python code for probability and population simulation modelled remote work trends effectively.
			    \item Presenting my work at the world finals at Jane Street New York enabled me to develop explanatory and communicative skills.
			\end{itemize}

%	\section{Awards}
%		\begin{itemize}
%			\item Computer Science, Physics GCSE school prizes
%			\item Computer Science, Mathematics Y12 prizes
%		\end{itemize}

%	\footnotetext[0]{Updated \today}
    \pagenumbering{gobble}
\end{document}

