% Derived from https://www.overleaf.com/project/614e77fa3f38da11edd45b16 Christopher Keyes

\documentclass{Resume}

\usepackage{enumitem}
\usepackage{etaremune}
\usepackage{amsmath}
\usepackage[colorlinks = true, linkcolor = blue, urlcolor = blue, citecolor = blue, anchorcolor = blue]{hyperref}


\begin{document}

\twocolumn[

\begin{@twocolumnfalse}

    \begin{center} \name{Hamish Starling} 

    \contact{hamishstarling@hotmail.co.uk}%{}{Github Link}}
    
\end{center}



\end{@twocolumnfalse}
]

	\section{Profile}
    An ambitious graduating 6th Form student, with a passion for mathematical and algorithmic problem solving, a constant desire to learn, and a curiosity to explore the use of mathematics and computing in industry.

%	\section{Academic Interests}
%	Briefly list your primary areas of academic interests here

	\section{Education}
		\subsection{Prospective Undergraduate Education}
			Next year I will begin a degree. I have offers to study:
				\begin{itemize}
					\item Computing (AI \& Machine Learning) at \\ \textbf{Imperial College London}
					\item Computer Science at \textbf{University College London}
					\item Data Science at \textbf{Warwick University}
%					\item Computer Science with Artificial Intelligence at\\ \textbf{University of Southampton}
				\end{itemize}	

		\subsection{6th Form - Watford Boys Grammar School}
				\begin{itemize}
					\item June 2021: A Level French (Self taught; \textbf{Grade A*})
					\item June 2022: A Level Physics (\textbf{Predicted A*}), Maths (\textbf{Predicted A*}), Further Maths (\textbf{Predicted A*}), \\Computer Science (\textbf{Predicted A*})
				\end{itemize}
				
		\subsection{Secondary - Watford Boys Grammar School}
				\begin{itemize}
					\item GCSE \textbf{Grade 9} in Mathematics, English Lang., French, Spanish, Geography, Biology, Physics, Chemistry, Computer Science, and \textbf{Grade 8} in English Lit.
					\item AQA Level 2 Certificate in Further Maths, \textbf{Grade 9}
				\end{itemize}
		\subsection{Cyber Discovery Summer School}
				Placing in the top 200 from 30000 students in the national programme, I attended three ``Elite" Summer Camps (2018-2020) and gained the GIAC-Certified Forensic Examiner (Digital Forensics) qualification, passing with 97 \%.


	\section{Skills}
			\begin{itemize}
				\item \textbf{Leadership \& Helping Others} As leader of my school's Computing Society, I taught sessions on IoT, Blockchain, REST APIs, Functional Programming, and many other topics to developing programmers in my school.
				\item \textbf{Organisation \& Teamwork} As project manager and chief programmer I led my team to win the Go4SET schools prize, creating an Android app to offer cheaper and healthier alternatives to the weekly shop. I organised the team to distribute roles fairly and logically and get the job done, under time and budget constraints.
				\item \textbf{Dedication \& Tenacity:}  It took 4 years of determined problem solving for me to finally achieve 1st equal placing in University of Southampton's National Cipher Challenge, using genetic and hill climbing algorithms to crack ciphers.
%				\item \textbf{Communication:} 
%				\item problem solvign
			\end{itemize}		

		\newpage
	\section{Programming Experience}
%		\subsection{Programming Languages}
			Self-taught in Python, C++, Haskell, HTML/JS/CSS, PHP and MySQL; passionate about learning new languages.

		\subsection{Competitive Programming}
%			\begin{itemize}
%				\item UK top 50 on \href{https://open.kattis.com/countries/GBR}{Kattis}
%				\item British Informatics Olympiad Participant last 5 years, top score 59.
%				\item Solved 29 problems on UVa Online Judge and over 80 on Advent of Code.
%			\end{itemize}
			I explore my love for algorithmic problem solving through programming competitions. 
			\begin{itemize}
			    \item \href{https://open.kattis.com/countries/GBR}{Kattis} UK top 50.
			    \item British Informatics Olympiad participant every year for the last 5 years.
			    \item Facebook Hacker Cup 2021 top 3000 and Google Code Jam top 3200.
			    
			\end{itemize}
		\subsection{Project Work}
			\begin{itemize}[itemsep=1mm, parsep=0pt]
				\item \textbf{Alexa Timetable App} for students at my school, web scraping data from Moodle and providing a Voice User Interface (VUI).
				\item \textbf{Recipes Website} for my household, with Optical Character Recognition (OCR) recipe input and saving of recipes via a Chrome Extension.
				\item \textbf{Machine Learning Python Programming IDE} using Recurrent Neural Networks and rule-based systems to improve students' Python programming. % Learnt why decent dev ops tools like docker are worth having - library version control + Releasing my own software and giving it logical version numbers
				\item \textbf{AI Chess and Hex games} with various AI strategies.
			\end{itemize}
			Interested in learning more about one of these projects? You can find them on my \href{https://github.com/starswap}{Github}.

	\section{Statistics \& Machine Learning}
	    My particular interest lies within the fields of Computational Statistics and Machine Learning, which I have explored through:
			
		\subsection{Online Courses}
			\begin{itemize}[itemsep=1mm, parsep=0pt]
				\item \textbf{Machine Learning} - Stanford University
				\item \textbf{Neural Networks \& Deep Learning} - \\ Deeplearning.ai 
				\item \textbf{Fundamentals of Reinforcement Learning}, University of Alberta (Part way through)
			\end{itemize}

		\subsection{Modelling \& Research Competition}
			\textbf{MathWorks Math Modelling Challenge 2022} 
			\\ Along with a team from my school, I was the UK winner of M3 Challenge 2022, receiving an Honourable Mention. Computationally calculating conditional probabilities and running a Monte Carlo simulation enabled us to model remote work trends effectively. Presenting my work at the competition final in New York enabled me to develop explanatory and communicative skills.

%	\section{Awards}
%		\begin{itemize}
%			\item Computer Science, Physics GCSE school prizes
%			\item Computer Science, Mathematics Y12 prizes
%		\end{itemize}

%	\footnotetext[0]{Updated \today}
    \pagenumbering{gobble}
\end{document}

