% Derived from https://www.overleaf.com/project/614e77fa3f38da11edd45b16 Christopher Keyes

\documentclass{Resume}

\usepackage{enumitem}
\usepackage{etaremune}
\usepackage{amsmath}
\usepackage[colorlinks = true, linkcolor = blue, urlcolor = blue, citecolor = blue, anchorcolor = blue]{hyperref}


\begin{document}

\twocolumn[

\begin{@twocolumnfalse}

    \begin{center} \name{Hamish Starling} 

    \contact{hamishstarling@hotmail.co.uk}%{\href{https://github.com/starswap}{Github Link}}
\end{center}



\end{@twocolumnfalse}
]

	\section{Profile}
    An ambitious final year A Level student, with a passion for mathematical and algorithmic problem solving, a constant desire to learn, and a curiosity to explore the use of mathematics and computing in industry.

%	\section{Academic Interests}
%	Briefly list your primary areas of academic interests here

	\section{Education}
		\subsection{Prospective Undergraduate Education}
			I have received offers to study
				\begin{itemize}
					\item Computing (AI \& Machine Learning) at \\ \textbf{Imperial College London}
					\item Computer Science at \textbf{University College London}
					\item Data Science at \textbf{Warwick University}
%					\item Computer Science with Artificial Intelligence at\\ \textbf{University of Southampton}
				\end{itemize}	

		\subsection{6th Form - Watford Boys Grammar School}
				\begin{itemize}
					\item June 2021: A Level French (Self taught; \textbf{Grade A*})
					\item June 2022: A Level Physics (\textbf{Predicted A*}), Maths (\textbf{Predicted A*}), Further Maths (\textbf{Predicted A*}), \\Computer Science (\textbf{Predicted A*})
				\end{itemize}
				
		\subsection{Secondary - Watford Boys Grammar School}
				\begin{itemize}
					\item GCSE \textbf{Grade 9} in Mathematics, English Lang., French, Spanish, Geography, Biology, Physics, Chemistry, Computer Science, and \textbf{Grade 8} in English Lit.
					\item AQA Level 2 Certificate in Further Maths, \textbf{Grade 9}
				\end{itemize}
		\subsection{Cyber Discovery Summer School}
				Placing in the top 200 from 30000 students in the national programme, I attended three ``Elite" Summer Camps (2018-2020) and gained the GIAC-Certified Forensic Examiner (Digital Forensics) qualification, passing with 97 \%.


	\section{Skills}
			\begin{itemize}
				\item \textbf{Leadership \& Helping Others} As leader of my school's Computing Society, I taught sessions on IoT, Blockchain, REST APIs, Functional Programming, and many other topics to developing programmers in my school. I also ran the Maths Club.
				\item \textbf{Organisation \& Teamwork} As project manager I led my team to win the Go4SET schools prize, creating an Android app to offer cheaper and healthier alternatives to the weekly shop. I organised the team to distribute roles fairly and logically and get the job done, under time and budget constraints.
				\item \textbf{Dedication and Tenacity:}  It took 4 years of determined problem solving for me to finally achieve 1st equal placing in University of Southampton's National Cipher Challenge with genetic and hill climbing algorithms using statistical analysis to crack ciphers.
%				\item \textbf{Communication:} 
%				\item problem solvign
			\end{itemize}		

		\newpage
	\section{Programming Experience}
%		\subsection{Programming Languages}
			Self-taught in Python, C++, Haskell, HTML/JS/CSS, PHP and MySQL; passionate about learning new languages.

		\subsection{Competitive Programming}
%			\begin{itemize}
%				\item UK top 50 on \href{https://open.kattis.com/countries/GBR}{Kattis}
%				\item British Informatics Olympiad Participant last 5 years, top score 59.
%				\item Solved 29 problems on UVa Online Judge and over 80 on Advent of Code.
%			\end{itemize}
			I explore my love for algorithmic problem solving through programming competitions. I rank in the \href{https://open.kattis.com/countries/GBR}{Kattis} UK top 50, and have participated in the British Informatics Olympiad every year for the last 5 years. I've completed 29 problems with the UVa Online Judge and over 80 on Advent of Code.
			
			Facebook + Google (Quantitative place nos not rounds. ) 

		\subsection{Project Work}
			\begin{itemize}[itemsep=1mm, parsep=0pt]
				\item \textbf{Alexa Timetable Skill} for students at my school, web scraping data from Moodle and providing a Voice User Interface (VUI).
				\item \textbf{Recipes Website} for my household, with Optical Character Recognition (OCR) recipe input and saving of recipes via a Chrome Extension.
				\item \textbf{Machine Learning Python Programming IDE} using Recurrent Neural Networks and rule-based systems to improve students' Python programming. % Learnt why decent dev ops tools like docker are worth having - library version control + Releasing my own software and giving it logical version numbers
				\item \textbf{AI Chess and Hex games} with Minimax and Monte Carlo strategies
			\end{itemize}

	\section{Mathematics and Data Science}
		I consistently achieve top-of-class marks in Maths, including full marks in my Y13 Mock A Level Further Statistics. I pursue greater mathematical understanding via:
		\subsection{Mathematics Competitions}
			\begin{itemize}[itemsep=1mm, parsep=0pt]
				\item 2021-22 Captain of WBGS Hans Woyda team
				\item UKMT Gold Award and Kangaroo Challenge for last 6 years
			\end{itemize}
		\subsection{Lectures and Masterclasses}
			For example the Royal Holloway Coulter McDowell Lecture 2020 and the RI Hertfordshire Mathematics Masterclasses, where I learnt about mathematically modelling the \\ Millennium Bridge and wildfires respectively.

		\subsection{Modelling \& Research Competition}
			MathWorks Math Modelling Challenge 2022 Honourable Mention \& UK Winner.
			
		\subsection{Online Courses}
			\begin{itemize}[itemsep=1mm, parsep=0pt]
				\item Stanford University Machine Learning, Coursera
				\item Deeplearning.ai Neural Networks \& Deep Learning
				\item University of Alberta Fundamentals of Reinforcement Learning, Coursera (Part way through)
			\end{itemize}


%	\section{Awards}
%		\begin{itemize}
%			\item Computer Science, Physics GCSE school prizes
%			\item Computer Science, Mathematics Y12 prizes
%		\end{itemize}

%	\footnotetext[0]{Updated \today}
    \pagenumbering{gobble}
\end{document}

